A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-27 manuscript.Rmd
write more lavaan helper

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r setup, include=FALSE}
library(repro)
source(here::here("R", "link.R"))
```

@@

It is probably better to assume more pessimistic values.
Therefore, we will assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.1.
These assumption can be simply translated into [`lavaan` [@lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

@@

```{r, results='asis', echo=FALSE}
model_truth <- paste(measurement(
  "MACH",
  paste0("x", 1:9),
  loadings = round(loadings_jones_paulhus * 0.7, 2)
),
intercepts("MACH", list(0, 0.1)),
collapse = "\n", sep = "\n")
cat("``` r",
    model_truth,
    "```",
    sep = "\n")
model <- paste(measurement(
  "MACH",
  paste0("x", 1:9)),
  intercepts("MACH", list(0, "NA")),
  sep = "\n")
```

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
  scripts:
    - R/lavaan_helper.R
    - R/simulation.R
    - R/link.R
csl: apa7.csl
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r setup, include=FALSE}
library(repro)
automate_load_scripts()
source(here::here("R", "link.R"))
```

@@

It is probably better to assume more pessimistic values.
This way, we make sure that our analytic strategy is viable even in non-optimal circumstances.
Therefore, we will assume that the loadings are 30% lower than reported and that the standardized mean difference is only 0.1.
These assumption can be simply translated into [`lavaan` [@lavaan]](https://lavaan.ugent.be)[^lavaan] model syntax:

@@

```{r, results='asis', echo=FALSE}
model_truth <- combine(
  measurement(
    "MACH",
    items("x", 9),
    loadings = round(loadings_jones_paulhus * 0.7, 2)
    ),
  intercepts("MACH", list(0, 0.1))
  )
cat("``` r",
    model_truth,
    "```",
    sep = "\n")
model <- combine(measurement(
  "MACH",
  items("x", 9)),
  intercepts("MACH", list(0, "NA")))
```
